### 2019-05-07 papers/haskell19/1-intro.tex
Work on Ale's feedback

% --------------------------------------
% Intro
%
Random property-based testing is a powerful technique for finding bugs
\cite{ArtsHNS15, HughesPAN16, HughesNSA16, MidtgaardJKNN17}.
%
In the Haskell community, QuickCheck is the predominant tool of this such
\cite{ClaessenH00}.
%
The developers specify
%
\begin{inparaenum}[(i)]
\item the testing properties their systems must fulfill, and
\item random data generators (or generators for short) for the data types
  involved at their properties.
\end{inparaenum}
%
Then, QuickCheck generates random seeds using these generators, which are used
to evaluate the system's properties in search of possible counterexamples, which
often indicate the presence of bugs.

@@

Using this representation, the example page \linebreak
%
\texttt{<html><b>hello<br>world!</b></html>}
%
is encoded as:
%
\begin{code}
Tag "html" $ Tag "b" $
  Text "hello" iJoin Sing "br" iJoin Text "world!"
\end{code} %$

@@

\begin{code}
instance Arbitrary Html where
  arbitrary = sized gen
    where  gen 0 = frequency
             [  (2,  Text    <$> arbitrary)
             ,  (1,  Sing    <$> arbitrary) ]
           gen d = frequency
             [  (2,  Text    <$> arbitrary)
             ,  (1,  Sing    <$> arbitrary)
             ,  (4,  Tag     <$> arbitrary  <*> gen (d-1))
             ,  (3,  Join    <$> gen (d-1)  <*> gen (d-1)) ]
\end{code} %$
%
At the top level, this definition parametrizes the generation process using
QuickCheck's |sized| combinator, which lets us build our generator via an
auxiliary local function |gen :: Int -> Gen Html|.
%
The |Int| passed to |gen| is known as the \emph{generation size}, and is
threaded seamlessly by QuickCheck on each call to arbitrary.
%
Then, we use this parameter to limit the maximum amount of recursive calls that
our generator can perform, and thus the maximum depth of the generated values.
%
If the generation size is positive (case |gen d|), our random generator picks a
random |Html| constructor with a given generation frequency (using QuickCheck's
|frequency| combinator), and proceeds to fill its fields using randomly
generated sub-terms---here using Haskell's applicative notation
\cite{Mcbride2008} and the default |Arbitrary| instance for |String|s.
%
For the case of the recursive sub-terms, this generator simply calls |gen|
recursively with a smaller generation size (|gen (d-1)|).
%
This process repeats until we reach the base case (|gen 0|) on each recursive
sub-term.
%
At this point, the generator is limited to pick only among terminal |Html|
constructors, hence ending the generation process.

% --------------------------------------
% Automatic derivation tools
%
As one can observe, the previous definition is quite mechanical, and depends
only on the generation frequencies we choose for each constructor.
%
Fortunately, there exists a variety of tools for obtaining random generators
automatically, based on the information encoded on the definition of the types
we want to generate.
%
Most of them implemented using Haskell's meta-programming framework named
Template Haskell \cite{SheardJ02}.
%
For instance, tools like \emph{MegaDeTH} or \emph{DRAGEN} will synthesize random
generators using roughly the same procedure as the one shown above.
%
On one hand, \emph{MegaDeTH} derives generators which simply pick among data
constructors with uniform probabilities, whereas \emph{DRAGEN} analyzes type
definitions, tuning the generation frequencies based on a predictive mechanism.
%
This allows the users to specify the desired distribution of values of the
derived generators.

% --------------------------------------
% Limitation
%
These tools provide a useful mechanism for automating the repetitive and
error-prone task of writing random generators by hand.
%
However, this simple derivation procedure, which
%
\begin{inparaenum}[(i)]
\item only considers the structural information encoded in type definitions, and
\item generates one single constructor at a time;
\end{inparaenum}
%
is often too generic to synthesize useful generators in practical scenarios.
%
For instance, because of the types we use for deriving our generators are too
general, leaving a large room for ill-formed values, e.g., invalid HTML pages;
or alternatively, because our properties need to be tested against very specific
input patterns in order to trigger bugs.

This problem, however, can be alleviated by considering additional sources of
structural information from our codebase other than just type definitions
\cite{Mista2019GeneratingRS}.
%
For instance, having a set of high-level combinators, defining an abstract
interface of our data types, e.g., |hr :: Html| or |bold :: Html -> Html|; it is
possible to include them into the generation process, thus obtaining more
complex and structured values.
%
In the same way, having functions defined using pattern matching over the data
types of our interest, e.g. |f (Join (Text t) (Tag s x)) = dots|, it is also
possible to include this rich structure which exposes a relationship among
different data constructors into our random generators.
%
This idea is addressed in depth in the next section, while the rest of this work
focuses on implementing it in a compositional way.

%
% Contributions
%
The main contribution of this paper are:
%
%
\begin{CompactItemize}
\item We identify some important limitations of performing random testing with
  automatically derived generators using state-of-the-art tools (Section
  \ref{sec:sources}).
\item We present an extensible mechanism for representing random values built
  upon different source constructions using Data Types \`a la Carte (Section
  \ref{sec:representation}).
\item We develop a modular generation schema, exploiting the composable nature
  of our representations, which are extended to encode information relevant to
  the generation process at the type level (Section \ref{sec:generators}).
\item We propose a simple type-level idiom for describing extensible generators,
  based on the types used to represent the desired shape of our random data
  (Section \ref{sec:typelevel}).\looseness=-1
\item We provide a Template Haskell tool%
  %
  \footnote{Link will be made available for the final version of this paper.}
  %
  for automatically deriving all the required machinery presented throughout
  this paper, and evaluate its generation performance using three real-world
  case studies (Section \ref{sec:casestudies}).
\end{CompactItemize}
%
Overall, we present a novel technique for reusing automatically derived
generators in a composable fashion, in contrast with the usual paradigm of
automatically deriving ``rigid'', monolithic generators.

>>>>

% --------------------------------------
% Intro
%
Random property-based testing is a powerful technique for finding bugs
\cite{ArtsHNS15, HughesPAN16, HughesNSA16, MidtgaardJKNN17}.
%
In the Haskell community, QuickCheck is the predominant tool for that task
\cite{ClaessenH00}.
%
The developers specify
%
\begin{inparaenum}[(i)]
\item the testing properties their systems must fulfill, and
\item random data generators (or generators for short) for the data types
  involved at their properties.
\end{inparaenum}
%
Then, QuickCheck generates random values using these generators, which are used
to evaluate the system's properties in search of possible counterexamples, which
often indicate the presence of bugs.

@@

Using this representation, the example page:

\begin{code}
ExampleHTML
\end{code}
%
can be encoded as:
%
\begin{code}
Tag "html" $ Tag "b" $
  Text "hello" iJoin Sing "br" iJoin Text "world!"
\end{code} %$

@@

\begin{code}
instance Arbitrary Html where
  arbitrary = sized gen
    where  gen 0 = frequency
             [  (2,  Text    <$> arbitrary)
             ,  (1,  Sing    <$> arbitrary) ]
           gen d = frequency
             [  (2,  Text    <$> arbitrary)
             ,  (1,  Sing    <$> arbitrary)
             ,  (4,  Tag     <$> arbitrary  <*> gen (d-1))
             ,  (3,  Join    <$> gen (d-1)  <*> gen (d-1)) ]
\end{code} %$
%
At the top level, this definition parametrizes the generation process using
QuickCheck's |sized| combinator, which lets us build our generator via an
auxiliary local function |gen :: Int -> Gen Html|.
%
The |Int| passed to |gen| is known as the \emph{generation size}, and is
threaded seamlessly by QuickCheck on each call to arbitrary.
%
Then, we use this parameter to limit the maximum amount of recursive calls that
our generator can perform, and thus the maximum depth of the generated values.
%
If the generation size is positive (case |gen d|), our random generator picks a
random |Html| constructor with a given generation frequency (using QuickCheck's
|frequency| combinator), and proceeds to fill its fields using randomly
generated sub-terms---here using Haskell's applicative notation
\cite{Mcbride2008} and the default |Arbitrary| instance for |String|s.
%
For the case of the recursive sub-terms, this generator simply calls the
function |gen| recursively with a smaller generation size (|gen (d-1)|).
%
This process repeats until we reach the base case (|gen 0|) on each recursive
sub-term.
%
At this point, the generator is limited to pick only among terminal |Html|
constructors, hence ending the generation process.

% --------------------------------------
% Automatic derivation tools
%
As one can observe, the previous definition is quite mechanical, and depends
only on the generation frequencies we choose for each constructor.
%
Fortunately, there exists a variety of tools for obtaining random generators
automatically, based on the information encoded on the definition of the types
we want to generate.
%
Most of them implemented using Haskell's meta-programming framework named
Template Haskell \cite{SheardJ02}.
%
For instance, tools like \emph{MegaDeTH} \cite{GriecoCB16, grieco2017} or
\emph{DRAGEN} \cite{DBLP:conf/haskell/MistaRH18} will synthesize random
generators using roughly the same procedure as the one shown above.
%
On one hand, \emph{MegaDeTH} derives generators which simply pick among data
constructors with uniform probabilities, whereas \emph{DRAGEN} analyzes type
definitions, tuning the generation frequencies based on a predictive mechanism.
%
This allows the users to specify the desired distribution of values of the
derived generators.
%
\looseness=-1

% --------------------------------------
% Limitation
%
These tools provide a useful mechanism for automating the repetitive and
error-prone task of writing random generators by hand.
%
However, this simple derivation procedure, which
%
\begin{inparaenum}[(i)]
\item only considers the structural information encoded in type definitions, and
\item generates one single constructor at a time;
\end{inparaenum}
%
is often too generic to synthesize useful generators in practical scenarios.
%
For instance, because of the types we use for deriving our generators are too
general, the generation process leaves a large room for ill-formed values, e.g.,
invalid HTML pages; or alternatively, because it fails at generating very
specific patterns of values which might be needed to trigger bugs.
%
% because our properties need to be tested against very specific input patterns in
% order to trigger bugs.

This problem, however, can be alleviated by considering additional sources of
structural information from our codebase other than just type definitions
\cite{Mista2019GeneratingRS}.
%
% For instance, having a set of high-level combinators, defining an abstract
% interface of our data types, e.g., |hr :: Html| or |bold :: Html -> Html|; it is
% possible to include them into the generation process, thus obtaining more
% complex and structured values.
%
For instance, it is possible to include into the generation process a set of
high-level combinators of our data types, e.g., |hr :: Html| or |bold :: Html ->
Html|---thus obtaining more complex and structured values.
%
This methodology of generating random data using high-level combinators has
shown to be particulary useful in the presence of monadic code
\cite{Claessen:2002, grieco2017}.
%
% In the same way, having functions defined using pattern matching over the data
% types of our interest, e.g. |f (Join (Text t) (Tag s x)) = dots|, it is also
% possible to include this rich structure which exposes a relationship among
% different data constructors into our random generators.
%
In the same way, it is possible to include into the generation process the
pattern matchings that different functions perform over the data types of our
interest, e.g. |f (Join (Text t) (Tag s x)) = dots|.
%
Such patterns often expose interesting relationships between multiple data
constructors, a valuable asset for testing complex systems expecting highly
structured inputs \cite{klein2009randomized}.
%
% This idea is addressed in depth in the next section, while the rest of this work
% focuses on implementing it in a compositional way.
%
This work shows how to modularly include these extra sources of structural
information into our automatically derived generators in a compositional manner.

%
% Contributions
%
The main contribution of this paper are:
%
\begin{CompactItemize}
\item We identify some important limitations of performing random testing with
  automatically derived generators using state-of-the-art tools (Section
  \ref{sec:sources}).
\item We present an extensible mechanism for representing random values built
  upon different sources of structural information using Data Types \`a la Carte
  (Section \ref{sec:representation}).
\item We develop a modular generation schema, exploiting the composable nature
  of our representations, which are extended to encode information relevant to
  the generation process at the type level (Section \ref{sec:generators}).
\item We propose a simple type-level idiom for describing extensible generators,
  based on the types used to represent the desired shape of our random data
  (Section \ref{sec:typelevel}).\looseness=-1
\item We provide a Template Haskell tool%
  %
  \footnote{Link will be made available for the final version of this paper.}
  %
  for automatically deriving all the required machinery presented throughout
  this paper, and evaluate its generation performance using three real-world
  case studies (Section \ref{sec:casestudies}).
\end{CompactItemize}
%
Overall, we present a novel technique for reusing automatically derived
generators in a composable fashion, in contrast with the usual paradigm of
automatically deriving ``rigid'', monolithic generators.

### 2019-05-07 papers/haskell19/2-sources.tex
Work on Ale's feedback

\section{Random Testing with Source Hints}
\label{sec:sources}

@@

% --------------------------------------
% Abstract interfaces
%
\subsection{Extracting Information From Interfaces}

@@

Note how difficult would it be to generate random values containing, for
example, structurally valid HTML lists if we only consider the structural
information encoded in our |Html| type definition.
%
After all, much of the valid structure of HTML has been encoded on its abstract
interface.

@@

% --------------------------------------
% Functions' pattern matchings
%
\subsection{Extracting Information From Patterns}

>>>>

\section{Additional Sources of Structural Information}
\label{sec:sources}

@@

% --------------------------------------
% Abstract interfaces
%
\subsection{Abstract Interfaces}

@@

Note how difficult it would be to generate random values containing, for
example, structurally valid HTML lists if we only consider the structural
information encoded in our |Html| type definition.
%
After all, much of the valid structure of HTML has been encoded on its abstract
interface.

@@

% --------------------------------------
% Functions' pattern matchings
%
\subsection{Pattern Matchings}

### 2019-05-07 papers/haskell19/3-representation.tex
Work on Ale's feedback

For this, we will define a set of different simple ``open'' types, each one in
charge of representing a single construction of our \emph{target} data type,
i.e., the actual data type we want to randomly generate.
%
These types can be later
%
\begin{inparaenum}[(i)]
\item combined in several ways depending on the desired shape of our test data,
  applying the familiar \`a la Carte technique;
\item randomly generated (see Section \ref{sec:generators}); and finally,
\item transformed back to the corresponding values of the target data type
  automatically.
\end{inparaenum}
%
This lifted representation of constructions can be automatically derived from
our source code in compile-time, relieving programmers of the burden of manually
implementing the required machinery.

@@

\begin{code}
eval :: Algebra f a => Fix f -> a
eval = alg . fmap eval . unFix
\end{code}
%
This function exploits the |Functor| structure of our representations,
unwrapping the fixed points and mapping their algebras to the result of
evaluating recursively each recursive sub-term.
%
This recusion schema using functors and F-Algebras to fold data generically has
been well studied and is known categorically a \emph{catamorphism} \tocite.

>>>>

For this, we will define a set of different simple ``open'' types, each one in
charge of representing a single construction of our \emph{target} data type,
i.e., the actual data type we want to randomly generate.
%
These types can be later
%
\begin{inparaenum}[(i)]
\item combined in several ways depending on the desired shape of our test data
  (applying the familiar \`a la Carte technique);
\item randomly generated (see Section \ref{sec:generators}); and finally,
\item transformed back to the corresponding values of the target data type
  automatically.
\end{inparaenum}
%
This lifted representation of constructions can be automatically derived from
our source code in compile-time, relieving programmers of the burden of manually
implementing the required machinery.

@@

\begin{code}
eval :: Algebra f a => Fix f -> a
eval = alg . fmap eval . unFix
\end{code}
%
This function exploits the |Functor| structure of our representations,
unwrapping the fixed points and mapping their algebras to the result of
evaluating recursively each recursive sub-term.
%
This recursion schema using functors and F-Algebras to fold data generically has
been well studied and is known a \emph{catamorphism} \cite{Meijer91}.

### 2019-05-07 papers/haskell19/6-casestudies.tex
Work on Ale's feedback

As we have shown in Section \ref{sec:generators}, the random generation
process we propose in this paper can be seen as having two phases.
%
First, we generate random values from the representation types used to specify
the shape of our data; and then we use their algebras to translate them to the
corresponding values of our target data types.
%
In particular, the transformation step is expected to pattern match repeatedly
against the |InL| and |InR| constructors of the |oplus| operators when
traversing each construction injection.
%
Because of this, in general, we expect a performance impact with respect to
manually-written concrete generators.

@@

\begin{table}[H]
  \begin{tabular}{||c||c||c||c||c||}
    \hline
    Case Study & \#|Con| & \#|Fun| & \#|Pat| & Total Constructions \\ \hline
    \hline
    RBT        & 2       & 5       & 6       & 13                  \\ \hline
    SExp       & 6       & -       & 9       & 15                  \\ \hline
    HTML       & 4       & 132     & -       & 136                 \\ \hline
  \end{tabular}
\end{table}

@@

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \begin{axis}
      [ height=6cm
      , width=9cm
      , ybar
      , ymajorgrids=true
      , ytick={0,1,...,4}
      , ymax=4
      , ymin=0.5
      , enlargelimits=0.25
      , enlarge x limits=0.25
      , /pgf/bar width=17pt
      , legend style={
        at={(0.5,-0.15)},
        anchor=north,legend columns=3}
      , legend image code/.code={%
        \draw[#1, draw=none] (0cm,-0.1cm) rectangle (0.3cm,0.2cm); }
      , ylabel={Relative Generation Time}
      , symbolic x coords={RBT, SExp, HTML}
      , xtick=data
      % , nodes near coords
      , nodes near coords align={vertical}
      ]
      \addplot[fill, red!30]   coordinates {(SExp,1)    (RBT,1)    (HTML,1)};
      \addplot[fill, green!30] coordinates {(SExp,2.40) (RBT,3.57) (HTML,4.27)};
      \addplot[fill, blue!30]  coordinates {(SExp,1.60) (RBT,2.52) (HTML,1.55)};
      \legend{Manual, Modular (lin), Modular (bal)}
    \end{axis}
  \end{tikzpicture}
  \caption{Generation time comparison between concrete and modular generators.}
  \label{fig:times}
\end{figure}
%
As it can be observed, our approach suffers from a noticeable runtime overhead
when using linearly defined representations, specially when considering the HTML
case study, involving a large number of constructions in the generation process.
%
However, we found that, by balancing our representation types, the generation
performance improves dramatically.
%
At the light of these improvements, our tool includes an additional type-level
computation that automatically balances our representations in order to reduce
the generation overhead.

>>>>

As we have shown in Section \ref{sec:generators}, the random generation
process we propose in this paper can be seen as having two phases.
%
First, we generate random values from the representation types used to specify
the shape of our data; and then we use their algebras to translate them to the
corresponding values of our target data types.
%
In particular, this last step is expected to pattern match repeatedly against
the |InL| and |InR| constructors of the |oplus| operators when traversing each
construction injection.
%
Because of this, in general, we expect a performance impact with respect to
manually-written concrete generators.

@@

\vspace{-5pt}
\begin{table}[H]
  \begin{tabular}{||c||c||c||c||c||}
    \hline
    Case Study & \#|Con| & \#|Fun| & \#|Pat| & Total Constructions \\ \hline
    \hline
    RBT        & 2       & 5       & 6       & 13                  \\ \hline
    SExp       & 6       & -       & 9       & 15                  \\ \hline
    HTML       & 4       & 132     & -       & 136                 \\ \hline
  \end{tabular}
\end{table}
\vspace{-5pt}

@@

\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \begin{axis}
      [ height=4.5cm
      , width=9cm
      , ybar
      , ymajorgrids=true
      , ytick={0,1,...,4}
      , ymax=3.7
      , ymin=0.7
      , enlargelimits=0.3
      , enlarge x limits=0.25
      , /pgf/bar width=17pt
      , legend style={
        at={(0.5,-0.2)},
        anchor=north,legend columns=3}
      , legend image code/.code={%
        \draw[#1, draw=none] (0cm,-0.1cm) rectangle (0.3cm,0.2cm); }
      , ylabel={Relative Generation Time}
      , symbolic x coords={RBT, SExp, HTML}
      , xtick=data
      % , nodes near coords
      , nodes near coords align={vertical}
      ]
      \addplot[fill, red!30]   coordinates {(SExp,1)    (RBT,1)    (HTML,1)};
      \addplot[fill, green!30] coordinates {(SExp,2.40) (RBT,3.57) (HTML,4.27)};
      \addplot[fill, blue!30]  coordinates {(SExp,1.60) (RBT,2.52) (HTML,1.55)};
      \legend{Manual, Modular (lin), Modular (bal)}
    \end{axis}
  \end{tikzpicture}
  \vspace{-7pt}
  \caption{Generation time comparison between concrete and modular generators.}
  \label{fig:times}
  \vspace{-18pt}
\end{figure}

As it can be observed, our approach suffers from a noticeable runtime overhead
when using linearly defined representations, specially when considering the HTML
case study, involving a large number of constructions in the generation process.
%
However, we found that, by balancing our representation types, the generation
performance improves dramatically.
%
At the light of these improvements, our tool includes an additional type-level
computation that automatically balances our representations in order to reduce
the generation overhead.

### 2019-05-07 papers/haskell19/7-related.tex
Work on Ale's feedback

\citeauthor{SwierstraDTC} \cite{SwierstraDTC} proposed Data Types \`a la Carte,
technique for building extensible data types and unified interpreters, as a
solution for the expression problem coined by \citeauthor{wadler1998expression}
\cite{wadler1998expression}.
%
In this work, we take ideas from this approach and extend them to work in the
scope of random data generation, where other parameters come into play apart
from just combining constructions, e.g., generation frequency and terminal
constructions.

@@

\emph{MegaDeTH} is a simple derivation tool that derives generators solely based
on their types, paying no attention whatsoever to the generation frequency of
each data constructor.
%
As a result, its automatically derived generators has been shown to be skewed
towards generating very small values\cite{DBLP:conf/haskell/MistaRH18}.

>>>>

\citeauthor{SwierstraDTC} proposed Data Types \`a la Carte \cite{SwierstraDTC},
a technique for building extensible data types, as a solution for the
\emph{expression problem}, coined by \citeauthor{wadler1998expression}
\cite{wadler1998expression}.
%
This technique has been successfully applied in a variety of scenarios, from
extensible compilers, to composable machine-mechanized proofs
\cite{Day:2013:CAL:2620678.2620680, persson2011generic, wu2014effect,
  delaware2013meta}.
%
In this work, we take ideas from this approach and extend them to work in the
scope of random data generation, where other parameters come into play apart
from just combining constructions, e.g., generation frequency and terminal
constructions.

@@

\emph{MegaDeTH} is a simple derivation tool that derives generators solely based
on their types, paying no attention whatsoever to the generation frequency of
each data constructor.
%
As a result, its automatically derived generators has been shown to be skewed
towards generating very small values
\cite{DBLP:conf/haskell/MistaRH18}.\looseness=-1

### 2019-05-07 papers/haskell19/8-conclusions.tex
Work on Ale's feedback

We presented a novel approach for automatically deriving flexible random
generators inspired by the seminal work on Data Types \`a la Carte.
%
Furthermore, we incorporate valuable structural information into our generation
process by considering not only data constructors, but also the information
statically available in abstract interfaces and functions' pattern matchings.

In the future, we aim to minimize the runtime overhead of our technique, using
perhaps prefix-free encodings based on generation frequencies, as a way to
reduce the representation bureaucracy as much as possible.
%
Additionally, we are interested on including additional sources of structural
information from the users' codebases, e.g., locally defined patterns or
sequences of functions applications.
%
Interesting thoughts to motivate our future research.

>>>>

We presented a novel approach for automatically deriving flexible random
generators inspired by the seminal work on Data Types \`a la Carte.
%
Furthermore, we incorporate valuable structural information into our generation
process by considering not only data constructors, but also the structural
information statically available in abstract interfaces and functions' pattern
matchings.

In the future, we aim to minimize the runtime overhead of our technique, using
perhaps prefix-free encodings based on generation frequencies, as a way to
reduce the representation bureaucracy as much as possible.
%
Additionally, we are interested on including additional sources of structural
information from the users' codebases, e.g., locally defined patterns or
sequences of functions applications---interesting thoughts to motivate our
future research.

### 2019-05-07 papers/haskell19/abstract.tex
Work on Ale's feedback

In this work, we develop an extensible framework for deriving compositional
generators, which can be easily combined in different ways in order to fit the
developers' demands, using a simple type-level description language.
%
Our framework relies on familiar ideas from the \`a la Carte technique for
writing composable interpreters in Haskell, extended with the machinery required
in the scope of random generation.
%
We provide an implementation of our ideas, and evaluate its performance using
real-world examples.

>>>>

In this work, we develop an extensible framework for deriving compositional
generators, which can be easily combined in different ways in order to fit the
developers' demands, using a simple type-level description language.
%
Our framework relies on familiar ideas from the \`a la Carte technique for
writing composable interpreters in Haskell.
%
In this light, we adapt this technique with the machinery required in the scope
of random generation.
%
We provide an implementation of our ideas, and evaluate its performance using
real-world examples.
%
